\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-05 paper/sp.tex
notes to self
bug fixes

% To-do items
% -----------
% - draft discussion
% - make sure we address the sensibleness and generality of the linear model for the photometric space
% - Coryn's point that we should carefully explain how our model is geometric.
% - related: HWR's point that this is standardizeable candles, like the Ia SNe results.
% - related: Put in an explanation of WHY this works so well.
% - related: Put in an explanation of how it is that we aren't really modeling luminosity or distance but really just generating parallaxes.
% - does the model need a cute name, like The Swan?
% - we need a Facilities list / tags
% - we need a Software list / tags
% - check with WISE experts that we have the correct WISE photometry

@@

% text macros
\newcommand{\equationname}{equation}
\newcommand{\code}[1]{\texttt{\detokenize{#1}}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et al.}}
\newcommand{\eg}{\foreign{e.g.}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\wise}{\project{\acronym{WISE}}}
\newcommand{\zmass}{\project{\acronym{2MASS}}}
\newcommand{\sdssiv}{\project{\acronym{SDSS-IV}}}
\newcommand{\sdssv}{\project{\acronym{SDSS-V}}}

@@

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$ for
every star $m$.
\tablename~\ref{tab:output} shows a snippet of this output, with the full output available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining the table to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \Gaia\ Archive (CITE).

>>>>

% To-do items
% -----------
% - draft discussion
% - make sure we address the sensibleness and generality of the linear model for the photometric space
% - Coryn's point that we should carefully explain how our model is geometric.
% - related: HWR's point that this is standardizeable candles, like the Ia SNe results.
% - related: Put in an explanation of WHY this works so well.
% - related: Put in an explanation of how it is that we aren't really modeling luminosity or distance but really just generating parallaxes.
% - does the model need a cute name, like The Swan?
% - check with WISE experts that we have the correct WISE photometry
% - we need an uncertainty estimate or noise model for our outputs.

@@

% text macros
\newcommand{\documentname}{\textsl{Article}}
\newcommand{\equationname}{equation}
\newcommand{\code}[1]{\texttt{\detokenize{#1}}}
\newcommand{\foreign}[1]{\textsl{#1}}
\newcommand{\etal}{\foreign{et al.}}
\newcommand{\eg}{\foreign{e.g.}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\apogee}{\project{\acronym{APOGEE}}}
\newcommand{\gaia}{\project{Gaia}}
\newcommand{\wise}{\project{\acronym{WISE}}}
\newcommand{\zmass}{\project{\acronym{2MASS}}}
\newcommand{\sdssiv}{\project{\acronym{SDSS-IV}}}
\newcommand{\sdssv}{\project{\acronym{SDSS-V}}}

@@

In the end, this method produces a spectrophotometric parallax estimate $\sparallax_m$ for
every star $m$.
\tablename~\ref{tab:output} shows a snippet of this output, with the full output available
as an electronic data table associated with this \documentname.
In order to use this output with \gaia\ astrometry, we recommend joining the table to the
\gaia\ Catalog on the \zmass\ ID (name), as per the instructions at the \gaia\ Archive (CITE).
In order to use this output with \apogee\ radial velocities and element abundances, we recommend
joining the table to the \sdssiv\ Catalog on the \zmass\ ID (name).
\begin{table}
\caption{The generated spectrophotometric parallaxes.\label{tab:output}}
\end{table}
